MLH1 Results Outline

### 2020-04-15 doc/Results_v2.rmd
starting clean results section

The high-recombination strains have significantly more DMC1 foci than the low-recombination strains in leptotene cells (t-test, p<**someSmallNumber** -- `r ttest.HighLow.L.pval`; one-way ANOVA, p = 0.00027 -- `r format(l.anova.pval, scientific=F)`). In contrast, the two strain groups do not differ in DMC1 foci counted in zygotene cells (later prophase)(t-test, p = 0.66 -- `r ttest.HighLow.Z.pval`). **note that this interpertation depends on which stage is most relevant to CO number**

>>>>

The high-recombination strains have significantly more DMC1 foci than the low-recombination strains in leptotene cells (t-test, p<**someSmallNumber** -- `r ttest.HighLow.L.pval`). In contrast, the two strain groups do not differ in DMC1 foci counted in zygotene cells (later prophase)(t-test, p = 0.66 -- `r ttest.HighLow.Z.pval`). **note that this interpertation depends on which stage is most relevant to CO number**
